On the error performance of the $A_n$ lattices

### 2012-04-29 double.tex
added Vaughan's biography edits

\begin{IEEEbiographynophoto}{I. Vaughan L. Clarkson}
was born in Brisbane, Queensland, Australia, in 1968. He received the
B.Sc. degree in mathematics and the B.E. degree
(Hons. I) in computer systems engineering from
The University of Queensland, Brisbane, in 1989
and 1990, respectively, and the Ph.D. degree in
systems engineering from The Australian National
University, Canberra, in 1997.

In 1988, he was with the Defence Science and Technology Organisation, Adelaide, Australia, first as a Cadet, later as a Professional Officer, and finally as a Research Scientist. From 1998 to 2000, he was a Lecturer at The University of Melbourne, Melbourne, Australia. From 2000 to 2008, he was a Senior Lecturer in the School of Information Technology and Electrical Engineering
at The University of Queensland. In 2008, he was promoted to Reader. In 2005,
he was a Visiting Professor in the Department of Electrical and Computer
Engineering, The University of British Columbia, Vancouver, Canada. His
research interests include statistical signal processing for communications and
defense, image processing, information theory, and lattice theory.
\end{IEEEbiographynophoto}

>>>>

\begin{IEEEbiographynophoto}{I. Vaughan L. Clarkson}
was born in Brisbane, Queensland, Australia, in 1968.  He received a B.Sc. in Mathematics and a B.E. (Hons. I) in Computer Systems Engineering from The University of Queensland, Brisbane, Australia, in 1989 and 1990, respectively, and a Ph.D. in Systems Engineering from The Australian National University, Canberra, Australia, in 1997.

Starting in 1988, he was employed by the Defence Science and Technology Organisation, Adelaide, Australia, first as a Cadet, later as a Professional Officer, and finally as a Research Scientist. From 1998 to 2000, he was a Lecturer at The University of Melbourne, Melbourne, Australia. From 2000 to 2008, he was a Senior Lecturer in the School of Information Technology and Electrical Engineering at The University of Queensland.  In 2008, he was promoted to Reader.  He was a Visiting Professor in the Department of Electrical and Computer Engineering at The University of British Columbia, Vancouver, Canada, in 2005 and at the Institute of Telecommunications, Technical University of Vienna, Austria, in 2012. His research interests include statistical signal processing for communications and defence, image processing, information theory and lattice theory.
\end{IEEEbiographynophoto}
